animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-29 animbook-journal.Rmd
figure widths and ChatGPT acknowledgement

```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package..", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
knitr::include_graphics("figures/NYT.png")
```

@@

```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
p <- wallaby_plot(object = animbook,
             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
             shade_palette = c("#737373", "#969696", "#BDBDBD",
                               "#D9D9D9","#D9D9D9","#D9D9D9"),
             rendering = "ggplot",
             subset = "top",
             relation = "one_many",
             total_point = NULL)

@@

I also acknowledge the use of ChatGPT (https://chat.openai.com/) to paraphrase the sentence.

>>>>

```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package..", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
knitr::include_graphics("figures/NYT.png")
```

@@

```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
p <- wallaby_plot(object = animbook,
             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
             shade_palette = c("#737373", "#969696", "#BDBDBD",
                               "#D9D9D9","#D9D9D9","#D9D9D9"),
             rendering = "ggplot",
             subset = "top",
             relation = "one_many",
             total_point = NULL)

@@

I also acknowledge the use of ChatGPT (https://chat.openai.com/) to improve the text, grammar and spelling.
